Word Learning as Network Growth: A Cross-linguistic Analysis

### 2018-07-06 journal/ms.Rmd
journal version

---
title: "Word Learning as Network Growth: A Cross-linguistic Analysis"

bibliography: library.bib
csl: apa6.csl
document-params: "10pt, letterpaper"

header-includes:
   - \usepackage[subtle]{savetrees}

author-information: > 
    \author{{\large \bf Abdellah Fourtassi} \\ \texttt{afourtas@stanford.edu} \\ Department of Psychology \\ Stanford University
    \And {\large \bf Yuan Bian} \\ \texttt{ybian.uiuc@gmail.com} \\ Department of Psychology \\ University of Illinois
    \And {\large \bf Michael C. Frank} \\ \texttt{mcfrank@stanford.edu} \\ Department of Psychology \\ Stanford University}

abstract:

    "Children tend to produce words earlier when they are connected to a variety of other words along both the phonological and semantic dimensions. Though this connectivity effect has been extensively documented, little is known about the underlying developmental mechanism.  One view suggests that learning is primarily driven by a network growth model where highly connected words in the child's early lexicon attract similar words. Another view suggests that learning is driven  by highly connected words in the external learning environment instead of highly connected words in the early internal lexicon. The present study tests both scenarios systematically in both the phonological and semantic domains, and across 8 languages. We show that external connectivity in the learning environment drives growth in both the semantic and the phonological networks, and that this pattern is consistent cross-linguistically. The findings suggest a word learning mechanism where children harness their statistical learning abilities to (indirectly) detect and learn highly connected words in the learning environment."

keywords:
    "semantic network, phonological network, network growth, mechanism of word learning"

output: cogsci2016::cogsci_paper
---

```{r global_options, include=FALSE}
rm(list=ls())

#knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.crop = F, fig.pos = "tb", fig.path='figs/',
#                      echo=F, warning=F, cache=F, message=F, sanitize = T)

knitr::opts_chunk$set(fig.width=3, fig.height=3, fig.pos = "tb", fig.path='figs/',
                      echo=F, warning=F, cache=F, message=F, sanitize = T)

```{r, libraries}
library(png)
library(grid)
library(ggplot2)
library(ggthemes)
library(xtable)
options(xtable.comment = FALSE)
library(purrr)
library(readr)
library(ggplot2)
library(langcog)
library(boot)
#library(lazyeval)
library(dplyr)
library(tidyr)
library(wordbankr)
library(directlabels)
#library(scales)
library(stringr)
library(lmtest)
library(rwebppl)
library(jsonlite)
library(nlme)
library(feather)
library(broom)
library(HDInterval)
library(BBmisc)
```

# Introduction

@@

While most studies have focused on the static properties of the lexical network, a few have investigated the underlying developmental process. In particular, @steyvers2005 suggested that the observed effects of connectivity are the consequence of how the lexical network gets constructed in the child's mind. According to this explanation, known as Preferential Attachment (PAT), highly connected words in the child's lexicon tend to "attract" more words over time, in a rich-get-richer scenario [@barabasi99]. In other words, what predicts word learning is the *internal* connectivity in the child's early lexicon. In contrast, @hills2009 suggested that what biases the learning is not the connectivity in the child's internal lexicon but, rather, *external* connectivity in the learning environment. They called this alternative explanation Preferential Acquisition (PAC).  Figure \ref{fig:growth} shows an illustration of both growth scenarios with the same simplified network. These two proposals represent two divergent ideas about the role of lexical networks in acquisition. On the PAT proposal, network structure is a causal factor in early word learning; in contrast, on the PAC approach, network structure is not internally represented and, therefore, might be an epiphenomenon of the statistics of the linguistic input.

```{r growth, fig.env = "figure", fig.pos = "H", fig.align='center', fig.width=3, fig.height=2, fig.cap = "\\label{fig:growth}Illustration of the growth scenarios. Filled circles (I1-I4) represent known words (internal), and empty circles (E1 and E2) represent words that have not been learned yet (external). Black lines represent links that are relevant in each growth scenario, and gray lines represent links that are irrelevant. For PAT, the utility of a candidate, external node is the average degree (i.e., number of links) of the internal nodes that it would attach to. Thus, according to PAT, the node E1 is more likely to enter the lexicon first. For PAC, the utility of a candidate node is its degree in the entire network. According to PAC, the node E2 is more likely to enter the lexicon first."}

img <- png::readPNG("figs/growth2.png")
grid::grid.raster(img)

@@

```{r }

#Import data from saved
data_all_scaled <- feather::read_feather("../saved_data/data_all_scaled.feather")

#tidy data
data_long <- data_all_scaled %>%
  gather(predictor, value, length:freq_mika)

data_long <- data_long %>%
  #filter(predictor %in% c("PAC_assoc", "PAC_phono_t2", "freq_mika", "length")) %>%
  filter(predictor %in% c("PAC_assoc", "PAC_phono_t2"))

data_long$predictor <- mapValues(data_long$predictor, 
                                 from = c("PAC_assoc", "PAC_phono_t2"), 
                                 to = c("Sem.", "Phono."))

#Compute the correlations 
correlations <-  data_long %>%
  group_by(language, predictor) %>%
  dplyr::summarise(cor = round(cor(AoA, value), 2))

plot_data_all <- ggplot(data_long, aes(x=value, y=AoA))+
  facet_grid(predictor ~ language)+#, scales = "free") +
  geom_jitter(#aes(colour = lexical_class),
    colour = solarized_palette(1),
    size = 0.5, alpha = 0.5) +
  geom_abline(slope = -1)+
  coord_cartesian(xlim=c(-1,5))+
  #scale_x_continuous(limits=c(-2,5))+
  scale_y_continuous(breaks =c(15,25,35))+
  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
  scale_colour_solarized(name = "") +
  theme_few()+
  #theme_bw()+
  theme(aspect.ratio = 0.7, 
        plot.margin=grid::unit(c(0,0,0,0), "mm")
        )+
  geom_text(data=correlations, aes(label=paste("r=", cor, sep="")), x=3.5, y=33, size=2, fontface = "bold")+
  xlab("degree z-score") +ylab("AoA")

ggsave("figs/data_all.png", plot = plot_data_all, width = 7, height = 3)

```{r all_data, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, fig.cap = "\\label{fig:data_all}Age of acquisition in the global network as predicted by the degree in this network. Results are shown in each language for phonological and semantic networks. Each point is a word, with lines indicating linear model fits."}
plot_data_all
#img <- png::readPNG("figs/data_all.png")
#grid::grid.raster(img)

```{r }

#Import data from saved
degreeDist <- feather::read_feather("../saved_data/degreeDist.feather") %>%
  dplyr::rename(Dimension = dimension)

plot_dist <- ggplot(data = degreeDist,  aes(x=x, y=y, col=Dimension))+
  facet_grid(. ~ language)+
  geom_point(size = 0.5, alpha = 0.5) +
  scale_y_log10() + scale_x_log10() +
  theme_few()+
  theme(aspect.ratio = 0.7,  text = element_text(size=9))+
  xlab("degree") +ylab("probability")

ggsave("figs/degreeDist.png", plot = plot_dist, width = 7, height = 3)

```{r degree_distribution, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3, fig.align = "center", strip.white=TRUE, fig.cap = "\\label{fig:degree_distribution}Log-log plot of the cumulative degree distribution function for the global phonological and semantic networks across languages. A perfect power-law distribution should appear as a straight line in this graph."}
plot_dist
#img <- png::readPNG("figs/data_all.png")
#grid::grid.raster(img)

@@

We obtained these nouns in eight languages: Croatian, Danish, English, Italian, Norwegian, Russian, Spanish, and Turkish. We used the subset of nouns that had entries in the Florida Association Norms (see below). Since these norms are available only in English, we used the hand-checked translation equivalents provided by @braginsky2016, allowing us to use the English association norms across languages. Table \ref{tab:stats} gives an overview of the data used. Translation equivalents were originally constructed for a subset of words appearing on the toddler CDI form, and so not all words are currently available. Note, however, that all languages have at least 60% of nouns translated.

@@

## Semantic networks

@@

<!--## Network growth

We tested two network growth scenarios discussed in @hills2009. The first one was *Preferential Attachment* (PAT). According to this mechanism, the network structure of known words predicts what words will be learned next. A word is more likely to be learned if it is linked to one of the highly connected nodes in this internal network. The second mechanism was *Preferential Acquisition* (PAC). In this model, what predicts what word will enter the lexicon is not connectivity in the internal network, but connectivity in the learning environment.  Figure \ref{fig:growth} shows an illustration of both growth scenarios with the same simplified network. For PAT, each candidate node was characterized with the average degree of the existing nodes that it would attach to. Thus, according to PAT, the node N1 is more likely to enter the lexicon first. For PAC, each candidate node was characterized with its degree in the entire network. According th PAC, the node N3 is more likely to enter the lexicon first.

-->

@@

@@

Connectivity in the global network is directly related to PAC as it represents the explicit criterion PAC uses to determine what words should be learned first (Figure \ref{fig:growth}). Therefore, a direct consequence of a PAC-like growth scenario is a correlation between connectivity in the global network and the age of acquisition.\footnote{This correlation is also compatible with PAT, although the causality is reversed. Indeed, from the perspective of this growth scenario, higher connectivity in the global network is caused by earlier learning, not the other way around. Some words end up being highly connected in the global network precisely because they happen to be acquired earlier and, therefore, have a higher chance of accumulating more links over time.} Figure \ref{fig:data_all} shows how the age of acquisition for each word varies as a function of its degree (or indegree for the semantic network). For ease of visual comparison, the predictor (i.e., the degree) was centered and scaled across languages. The plots show, overall, a negative correlation between the month of acquisition and the degree, indicating that nouns with higher degrees are generally learned earlier.

###Power-law degree distribution?
We also analyzed the global network's degree distribution. The shape of this distribution is particularly relevant to PAT as this growth scenario is known to generate networks with a power-law degree distribution [i.e., a distribution of the form $p(k) \propto \frac{1}{k^{\alpha}}$, @barabasi99]. If the network displays this property, this fact would suggest a PAT-like generative process. Conversely, if the degree distribution does not follow a power law, this fact would weaken the case for PAT. The log-log plots are shown in Figure \ref{fig:degree_distribution}. We fit a power law to each empirical degree distribution following the procedure outlined in @clauset09 and using the related R package [poweRlaw, @gillespie15]. In brief, the analysis consisted in two steps. First, we derived the optimal cut-off, $k_{min}$, above which the distribution is more likely to follow a power law,\footnote{In natural phenomena, it is often the case that the power law applies only for values above a certain minimum.} and we estimate the corresponding scaling parameter $\alpha$. Second we calculated the goodness-to-fit, which resulted in a $p$-value quantifying the plausibility of the model. Overall, we could not reject the null hypothesis of a power-law distribution: the $p$-value was generally above 0.1, except for the Italian phonological network where we obtained  $p < 0.05$, suggesting that the power law can be ruled out in this particular case.

In sum, the static properties of the global network are *a priori* compatible with both PAT and PAC. In order to decide between these two developmental scenarios, we need to fit explicit growth models to the data.
<!--
```{r }

#Import data from saved
post_combined <- feather::read_feather("../saved_data/combined_net.feather")

pred_comb <- ggplot(post_combined, aes(x = model, y = mean)) +
  geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, y = mean, col = model), size=0.3)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  coord_flip() +
  facet_wrap(~language, ncol=4)  +
  guides(colour=FALSE)+
  scale_colour_solarized() +
  theme_bw()+
  theme(aspect.ratio = 0.7)

ggsave("figs/pred_comb.png", plot = pred_comb, width = 8, height = 4)
```

```{r pred_comb_img, fig.env = "figure*", fig.pos = "h", fig.width=6, fig.height=3, fig.align = "center", fig.cap = "\\label{fig:pred_comb_img}Estimates of the growth models' parameters in each language. Dots represent the means of the posteriori distribution of the parameters, and ranges represent 95\\% credible intervals (computed using the highest density intervals). "}
pred_comb
#img <- png::readPNG("figs/pred_comb.png")
#grid::grid.raster(img)
```
-->

```{r }

#Import data from saved
individual <- feather::read_feather("../saved_data/individual_both.feather") %>%
  filter(Evaluation =='Fit') %>%
  select(-Evaluation) %>%
  mutate(Test = 'Individual')

combined <- feather::read_feather("../saved_data/combined_net.feather") %>%
  dplyr::rename(lower = hdi_lower,
                upper = hdi_upper) %>%
  mutate(Test = 'Combined')

growth_all <- bind_rows(individual, combined)

pred_ind <- ggplot(growth_all, aes(x = model , y = mean)) +
  geom_pointrange(aes(ymin = lower, ymax = upper, col = model, linetype=Test),
                  position = position_dodge(width = .5),
                  size = 0.5,
                  fatten = 0.5)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  coord_flip() +
  facet_wrap(~language, ncol=4)  +
  guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.3)))+
  scale_colour_solarized() +
  theme_few()+
  theme(aspect.ratio = 0.7, axis.text.x = element_text(size=8))

ggsave("figs/pred_ind.png", plot = pred_ind, width = 8, height = 4)

@@

```{r pred_ind_img, fig.env = "figure*", fig.pos = "h", fig.width=7, fig.height=3.5, fig.align = "center", fig.cap = "\\label{fig:pred_ind}Evaluation of network growth scenarios both individually (dotted), and when combined in the same growth model (solid). Each dot represents the mean of the posterior distribution of the corresponding growth parameter, with ranges representing 95\\% credible intervals (computed using the highest density intervals). Positive values mean that learning proceeds according to the predictions of the growth scenario. Negative values mean that learning proceeds in opposition to the predictions of the growth scenario."}

pred_ind

#img <- png::readPNG("figs/pred_ind.png")
#grid::grid.raster(img)
```

@@

\noindent where $\beta$ is a fitted parameter that captures the magnitude of the relationship between network parameters and growth (analogous to a regression coefficient). A positive value of $\beta$ means that words with higher growth values $d_i$ are acquired first, and a negative value means that words with lower growth values are acquired first (see Figure \ref{fig:growth} for an illustration of how growth values $d_i$ are defined in each growth scenario). The normalization includes all words that could be learned at that month.

We estimated the parameter $\beta$ using a Bayesian approach. The inference was performed using the probabilistic programming language  WebPPL [@dippl]. We defined a uniform prior over $\beta$, and at each month, we computed the likelihood function over words that could possibly enter the lexicon at that month, fit to the words that have been learned at that month (using formula 1). Markov Chain Monte Carlo sampling resulted in a posterior distribution over $\beta$, which we summarized in Figure \ref{fig:pred_ind}.

<!--Besides fitting a growth model to the data, we conducted a separate evaluation. This second evaluation consists in determining, in each month, the growth value distribution of all words that could possibly be learned at this month, and then computing the z-score of each learned word with respect to this distribution.  For each growth scenario, we tested if the distribution constituted by the z-scores of all learned words was different from zero, using a one-sample t-test.-->

<!--The results from both evaluations were very similar and lead essentially to the same conclusions.\footnote{We do not show here the results of the second evaluation because they were redundant with the results of the first evaluation}-->For the semantic networks, the results replicate Hills et al.'s finding in English, which is that the semantic network grows by PAC, not by PAT. Moreover, this finding holds in seven of the eight languages we examined.\footnote{One could imagine that the fact of using English free association norms cross-linguistically would decrease the effect of non-English semantic networks because of possible cultural differences. However, our findings do not support this assumption as the effects were generally similar in magnitude cross-linguistically.} The PAC model also fits better than PAT for phonological networks. We note however that PAT, though weaker, fares  better for the phonological networks (where it predicts part of the growth process in some languages such as Croatian, English, Norwegian and Russian) than it does for the semantic networks (where it is rather universally unpredictive).

@@

```{r }

#Import data from saved
regressions <- feather::read_feather("../saved_data/regressions_bis.feather")

pred_regressions <- ggplot(regressions, aes(x = predictor, y = estimate)) +
  geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., y = estimate, col = predictor), size=0.3)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  facet_wrap(~language, ncol=4)  +
  coord_flip() +
  guides(colour=FALSE)+
  scale_colour_solarized() +
  theme_few()+
  theme(aspect.ratio = 0.7)

ggsave("figs/pred_regressions.png", plot = pred_regressions, width = 8, height = 4)
```

```{r regressions_img, fig.env = "figure*", fig.pos = "h", fig.width=6, fig.height=3, fig.align = "center", fig.cap = "\\label{fig:regressions_img}Estimates of predictor coefficients by language, with ranges indicating 95\\% confidence intervals. Positive values indicate a positive relationship (e.g. longer words tend to have a higher AoA), while negative values indicate a negative relationship (e.g. words with higher frequency tend to have a lower AoA)."}

pred_regressions

#img <- png::readPNG("figs/pred_regressions.png")
#grid::grid.raster(img)
```

@@

```{r }

#Import data from saved
regression_all <- feather::read_feather("../saved_data/regression_all_bis.feather")
regression_all_noCov <- feather::read_feather("../saved_data/regression_all_bis_noCov.feather")

>>>>

---
title             : "Word Learning as Network Growth: A Cross-linguistic Analysis"
shorttitle        : "Word Learning as Network Growth"
#numbersections: true

author: 
  - name          : "Abdellah Fourtassi"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "afourtas@stanford.edu"

  - name          : "Yuan Bian"
    affiliation   : "2"
    email         : "ybian.uiuc@gmail.com"

  - name          : "Michael C. Frank"
    affiliation   : "1"
    email         : "mcfrank@stanford.edu"

affiliation:
  - id            : "1"
    institution   : "Department of Psychology, Stanford University"

  - id            : "2"
    institution   : "Department of Psychology, University of Illinois"

author_note: |

  Abdellah Fourtassi

  Department of Psychology

  Stanford University

  50 Serra Mall

  Jordan Hall, Building 420

  Stanford, CA 94301

abstract: |

 Children tend to produce words earlier when they are connected to a variety of other words along both the phonological and semantic dimensions. Though this connectivity effect has been extensively documented, little is known about the underlying developmental mechanism.  One view suggests that learning is primarily driven by a network growth model where highly connected words in the child's early lexicon attract similar words. Another view suggests that learning is driven  by highly connected words in the external learning environment instead of highly connected words in the early internal lexicon. The present study tests both scenarios systematically in both the phonological and semantic domains, and across 8 languages. We show that external connectivity in the learning environment drives growth in both the semantic and the phonological networks, and that this pattern is consistent cross-linguistically. The findings suggest a word learning mechanism where children harness their statistical learning abilities to (indirectly) detect and learn highly connected words in the learning environment.

keywords          : "Language understanding; audio-visual processing; word learning; speech perception; computational modeling."

header-includes:
   #- \usepackage{bibentry}
   - \usepackage[sortcites=false,sorting=none]{biblatex}

bibliography      : ["references.bib"]

figsintext        : yes
figurelist        : no
tablelist         : no
footnotelist      : no
lineno            : yes

lang              : "english"
class             : "man"
output            : papaja::apa6_pdf

citation_package: biblatex

---

```{r}
knitr::opts_chunk$set(echo=F, warning=F, cache=F, message=F, sanitize = T)
```

```{r load_packages, include = FALSE}
library(papaja)
library(readr)
library(tidyr)
library(ggplot2)
library(cowplot)
library(knitr)
library(boot)
library(dplyr)
library(langcog)
library(ggthemes)
library(broom)
library(HDInterval)
#library("knitcitations")
#cleanbib()
#options("citation_format" = "pandoc")
```

#Introduction

@@

While most studies have focused on the static properties of the lexical network, a few have investigated the underlying developmental process. In particular, @steyvers2005 suggested that the observed effects of connectivity are the consequence of how the lexical network gets constructed in the child's mind. According to this explanation, known as Preferential Attachment (PAT), highly connected words in the child's lexicon tend to "attract" more words over time, in a rich-get-richer scenario [@barabasi99]. In other words, what predicts word learning is the *internal* connectivity in the child's early lexicon. In contrast, @hills2009 suggested that what biases the learning is not the connectivity in the child's internal lexicon but, rather, *external* connectivity in the learning environment. They called this alternative explanation Preferential Acquisition (PAC).  Figure\ \@ref(fig:growth) shows an illustration of both growth scenarios with the same simplified network. These two proposals represent two divergent ideas about the role of lexical networks in acquisition. On the PAT proposal, network structure is a causal factor in early word learning; in contrast, on the PAC approach, network structure is not internally represented and, therefore, might be an epiphenomenon of the statistics of the linguistic input.

```{r growth, fig.cap = "Illustration of the growth scenarios. Filled circles (I1-I4) represent known words (internal), and empty circles (E1 and E2) represent words that have not been learned yet (external). Black lines represent links that are relevant in each growth scenario, and gray lines represent links that are irrelevant. For PAT, the utility of a candidate, external node is the average degree (i.e., number of links) of the internal nodes that it would attach to. Thus, according to PAT, the node E1 is more likely to enter the lexicon first. For PAC, the utility of a candidate node is its degree in the entire network. According to PAC, the node E2 is more likely to enter the lexicon first.", fig.align = "center", out.width = "400px"}
knitr::include_graphics("figs/growth2.png")
```

@@

@@

We obtained these nouns in eight languages: Croatian, Danish, English, Italian, Norwegian, Russian, Spanish, and Turkish. We used the subset of nouns that had entries in the Florida Association Norms (see below). Since these norms are available only in English, we used the hand-checked translation equivalents provided by @braginsky2016, allowing us to use the English association norms across languages. Table \@ref(tab:stats) gives an overview of the data used. Translation equivalents were originally constructed for a subset of words appearing on the toddler CDI form, and so not all words are currently available. Note, however, that all languages have at least 60% of nouns translated.

@@

# Semantic networks

@@

@@

```{r}
#Import data from saved
data_all <- feather::read_feather("../saved_data/data_static_scaled.feather")

data_long <- data_all %>%
  rename(Sem = sem_deg, Phono=phono_deg) %>%
  gather(predictor, value, Sem:frequency) %>%
  filter(predictor == "Sem" | predictor == "Phono")

correlations <- data_long %>%
  group_by(measure, language, predictor) %>%
  summarise(cor = round(cor(aoa, value), 2))

plot_correlation_prod <- ggplot(subset(data_long, measure == "produces"), aes(x=value, y=aoa))+
  facet_grid(predictor ~ language)+#, scales = "free") +
  geom_jitter(#aes(colour = lexical_class),
    colour = solarized_palette(1),
    size = 0.5, alpha = 0.5) +
  geom_abline(slope = -1)+
  coord_cartesian(xlim=c(-1,5))+
  #scale_x_continuous(limits=c(-2,5))+
  scale_y_continuous(breaks =c(15,25,35))+
  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
  scale_colour_solarized(name = "") +
  theme_few()+
  #theme_bw()+
  theme(aspect.ratio = 0.7, 
        plot.margin=grid::unit(c(0,0,0,0), "mm")
        )+
  geom_text(data=subset(correlations, measure=="produces"), aes(label=paste("r=", cor, sep="")), x=3.5, y=33, size=2, fontface = "bold")+
  xlab("degree z-score") +ylab("Age")

plot_correlation_comp <- ggplot(subset(data_long, measure == "understands"), aes(x=value, y=aoa))+
  facet_grid(predictor ~ language)+#, scales = "free") +
  geom_jitter(#aes(colour = lexical_class),
    colour = solarized_palette(1),
    size = 0.5, alpha = 0.5) +
  geom_abline(slope = -1)+
  coord_cartesian(xlim=c(-1,5))+
  #scale_x_continuous(limits=c(-2,5))+
  scale_y_continuous(breaks =c(15,25,35))+
  geom_smooth(method = "lm", colour = "grey3", se=FALSE)+
  scale_colour_solarized(name = "") +
  theme_few()+
  #theme_bw()+
  theme(aspect.ratio = 0.7, 
        plot.margin=grid::unit(c(0,0,0,0), "mm")
        )+
  geom_text(data=subset(correlations, measure=="understands"), aes(label=paste("r=", cor, sep="")), x=3.5, y=33, size=2, fontface = "bold")+
  xlab("degree z-score") +ylab("Age")

#ggsave("figs/plot_correlation_prod.pdf", plot = plot_correlation_prod, width = 10, height = 3)
#ggsave("figs/plot_correlation_comp.pdf", plot = plot_correlation_comp, width = 10, height = 3)
```

```{r corrAll, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Age of production (A) and comprehension (B) in the global network as predicted by the degree in this network. Results are shown in each language for phonological and semantic networks. Each point is a word, with lines indicating linear model fits."}

plot_grid(plot_correlation_prod , NULL, plot_correlation_comp , labels = c("A", "", "B"), ncol = 1, align = "v", rel_heights = c(1.3, 0.1, 1.3))

@@

Connectivity in the global network is directly related to PAC as it represents the explicit criterion PAC uses to determine what words should be learned first (Figure \@ref(fig:growth)). Therefore, a direct consequence of a PAC-like growth scenario is a correlation between connectivity in the global network and the age of acquisition.\footnote{This correlation is also compatible with PAT, although the causality is reversed. Indeed, from the perspective of this growth scenario, higher connectivity in the global network is caused by earlier learning, not the other way around. Some words end up being highly connected in the global network precisely because they happen to be acquired earlier and, therefore, have a higher chance of accumulating more links over time.} Figure \@ref(fig:corrAll) shows how the age of production (A) and comprehension (B) for each word varies as a function of its degree (or indegree for the semantic network). For ease of visual comparison, the predictor (i.e., the degree) was centered and scaled across languages. The plots show, overall, a negative correlation between the month of acquisition and the degree, indicating that nouns with higher degrees are generally learned earlier.

```{r}

degree_dist <- feather::read_feather("../saved_data/degree_dist.feather") %>%
  mutate(data=ifelse(measure=='produces', 'Prod.', 'Comp.'))

plot_degree <- ggplot(data = degree_dist,  aes(x=x, y=y, col=dimension))+
  facet_grid(data ~ language)+#, scales = "free") +
  geom_point(#aes(colour = lexical_class),
    #colour = solarized_palette(1),
    size = 0.5, alpha = 0.5) +
  scale_y_log10() + scale_x_log10() +
  theme(aspect.ratio = 1) +
  theme_few()+
  theme(aspect.ratio = 0.7)+
  xlab("Degree") +ylab("Prob.")

ggsave("figs/plot_degree.pdf", plot = plot_degree, width = 10, height = 3)
```

```{r degreeDist, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Log-log plot of the cumulative degree distribution function for the global phonological and semantic networks across languages. The figure shows the results for both production and comprehension data. A perfect power-law distribution should appear as a straight line in this graph."}

knitr::include_graphics("figs/plot_degree.pdf")

@@

###Power-law degree distribution?
We also analyzed the global network's degree distribution. The shape of this distribution is particularly relevant to PAT as this growth scenario is known to generate networks with a power-law degree distribution [i.e., a distribution of the form $p(k) \propto \frac{1}{k^{\alpha}}$, @barabasi99]. If the network displays this property, this fact would suggest a PAT-like generative process. Conversely, if the degree distribution does not follow a power law, this fact would weaken the case for PAT. The log-log plots are shown in Figure \@ref(fig:degreeDist). We fit a power law to each empirical degree distribution following the procedure outlined in @clauset09 and using the related R package [poweRlaw, @gillespie15]. In brief, the analysis consisted in two steps. First, we derived the optimal cut-off, $k_{min}$, above which the distribution is more likely to follow a power law,\footnote{In natural phenomena, it is often the case that the power law applies only for values above a certain minimum.} and we estimate the corresponding scaling parameter $\alpha$. Second we calculated the goodness-to-fit, which resulted in a $p$-value quantifying the plausibility of the model. The results are shown in Appendix 1, table XX. Overall, we could not reject the null hypothesis of a power-law distribution: the $p$-value was generally above 0.1.

In sum, the static properties of the global network are *a priori* compatible with both PAT and PAC. In order to decide between these two developmental scenarios, we need to fit explicit growth models to the data.

```{r}

growth_preds <- feather::read_feather("../saved_data/growth_preds.feather")

plot_growth_preds_prod <- ggplot(subset(growth_preds, measure == "produces"), aes(x = model , y = mean)) +
  geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, col = model, linetype=Test),
                  position = position_dodge(width = .5),
                  size = 0.5,
                  fatten = 0.5)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  coord_flip() +
  facet_wrap( ~ language, ncol=5) +
  guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.3)))+
  scale_colour_solarized() +
  theme_few()+
  theme(aspect.ratio = 0.7)

plot_growth_preds_comp <- ggplot(subset(growth_preds, measure == "understands"), aes(x = model , y = mean)) +
  geom_pointrange(aes(ymin = hdi_lower, ymax = hdi_upper, col = model, linetype=Test),
                  position = position_dodge(width = .5),
                  size = 0.5,
                  fatten = 0.5)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  coord_flip() +
  facet_wrap( ~ language, ncol=5) +
  guides(colour=FALSE, linetype = guide_legend(override.aes = list(size=0.3)))+
  scale_colour_solarized() +
  theme_few()+
  theme(aspect.ratio = 0.7)

#ggsave("figs/plot_growth_preds_prod.pdf", plot = plot_growth_preds_prod, width = 10, height = 4)
#ggsave("figs/plot_growth_preds_comp.pdf", plot = plot_growth_preds_comp, width = 10, height = 4)

```{r growthPred, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Evaluation of network growth scenarios, for both A) production and B) comprehension. We plot values when predictors are evaluted individually (dotted), and when combined in the same growth model (solid). Each dot represents the mean of the posterior distribution of the corresponding growth parameter, with ranges representing 95\\% credible intervals (computed using the highest density intervals). Positive values mean that learning proceeds according to the predictions of the growth scenario. Negative values mean that learning proceeds in opposition to the predictions of the growth scenario."}

legend <- get_legend(plot_growth_preds_prod)

plot_noLegend <- plot_grid(plot_growth_preds_prod + theme(legend.position="none"), NULL, plot_growth_preds_comp + theme(legend.position="none"), labels = c("A", "", "B"), ncol = 1, align = "v", rel_heights = c(1.3, 0.1, 1.3))

plot_grid(plot_noLegend, legend, rel_widths = c(2, .2))

#knitr::include_graphics("figs/plot_growth_preds_prod.pdf")

@@

\noindent where $\beta$ is a fitted parameter that captures the magnitude of the relationship between network parameters and growth (analogous to a regression coefficient). A positive value of $\beta$ means that words with higher growth values $d_i$ are acquired first, and a negative value means that words with lower growth values are acquired first (see Figure \@ref(fig:growth) for an illustration of how growth values $d_i$ are defined in each growth scenario). The normalization includes all words that could be learned at that month.

We estimated the parameter $\beta$ using a Bayesian approach. The inference was performed using the probabilistic programming language  WebPPL [@dippl]. We defined a uniform prior over $\beta$, and at each month, we computed the likelihood function over words that could possibly enter the lexicon at that month, fit to the words that have been learned at that month (using formula 1). Markov Chain Monte Carlo sampling resulted in a posterior distribution over $\beta$, which we summarized in Figure \@ref(fig:growthPred).

For the semantic networks, the results replicate Hills et al.'s finding in English, which is that the semantic network grows by PAC, not by PAT. Moreover, this finding holds in seven of the eight languages we examined.\footnote{One could imagine that the fact of using English free association norms cross-linguistically would decrease the effect of non-English semantic networks because of possible cultural differences. However, our findings do not support this assumption as the effects were generally similar in magnitude cross-linguistically.} The PAC model also fits better than PAT for phonological networks. We note however that PAT, though weaker, fares  better for the phonological networks (where it predicts part of the growth process in some languages such as Croatian, English, Norwegian and Russian) than it does for the semantic networks (where it is rather universally unpredictive).

```{r}
static_preds <- feather::read_feather("../saved_data/static_preds.feather")

plot_static_preds_prod <- ggplot(subset(static_preds, measure =="produces"), aes(x = predictor, y = estimate)) +
  geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., y = estimate, col = predictor, linetype=Test), 
                  position = position_dodge(width = .5),
                  size = 0.5,
                  fatten = 0.5)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  facet_wrap(~language, ncol=5)  +
  coord_flip() +
  guides(colour=FALSE)+
  scale_colour_solarized() +
  theme_few()+
  theme(aspect.ratio = 0.7)

plot_static_preds_comp <- ggplot(subset(static_preds, measure =="understands"), aes(x = predictor, y = estimate)) +
  geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., y = estimate, col = predictor, linetype=Test),
                  position = position_dodge(width = .5),
                  size = 0.5,
                  fatten = 0.5)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  facet_wrap(~language, ncol=5)  +
  coord_flip() +
  guides(colour=FALSE)+
  scale_colour_solarized() +
  theme_few()+
  theme(aspect.ratio = 0.7)

```{r staticPred, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Estimates of predictor coefficients by language in production (A) and comprehension (B), with ranges indicating 95\\% confidence intervals. Positive values indicate a positive relationship (e.g. longer words tend to have a higher AoA), while negative values indicate a negative relationship (e.g. words with higher frequency tend to have a lower AoA)."}

legend <- get_legend(plot_static_preds_prod)

plot_noLegend <- plot_grid(plot_static_preds_prod + theme(legend.position="none"), NULL, plot_static_preds_comp + theme(legend.position="none"), labels = c("A", "", "B"), ncol = 1, align = "v", rel_heights = c(1.3, 0.1, 1.3))

plot_grid(plot_noLegend, legend, rel_widths = c(2, .2))

#plot_static_preds_prod

@@

```{r}
static_preds_all <- feather::read_feather("../saved_data/static_preds_all.feather")

plot_static_preds_all <- ggplot(static_preds_all, aes(x = predictor, y = Estimate)) +
  geom_pointrange(aes(ymin = X2.5.., ymax = X97.5.., y = Estimate, col = predictor, linetype=Test),
                  position = position_dodge(width = .5),
                  size = 0.5,
                  fatten = 0.5)+
  geom_hline(yintercept = 0, color = "grey", linetype = "dashed")+
  facet_wrap(~measure)  +
  coord_flip() +
  guides(colour=FALSE)+
  scale_colour_solarized() +
  theme_few()+
  theme(aspect.ratio = 0.7)

ggsave("figs/plot_static_preds_all.pdf", plot = plot_static_preds_all, width = 6, height = 3)

```{r staticAll, out.width = "\\textwidth", fig.pos = "!h", fig.cap = "Estimates of predictor coefficients in the combined mixed-effect model with language as a random effect for both production and comprehension. Ranges indicate 95\\% confidence intervals. Lighter points indicate estimates of PAC predictors in a model that does not include frequency and length as covariates."}

knitr::include_graphics("figs/plot_static_preds_all.pdf")

@@
